Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
Sec. 4

After each task, we update $\mathcal{M}$, and we can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s \in \{1, \ldots, t-1 \}$. This means that for training  the successive task, the new objective to minimize becomes $\weights_t^* = \arg\min_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \, \mathcal{R}_\textrm{\our}(\weights, \mathcal{M})$, with the regularizer
%
\begin{equation}\label{eq-cl-regularizer}
  \mathcal{R}_\mathrm{\our}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \frac{1}{M} 
	\left\lVert 
	f_{\weights}(\MZ_{s}) - \vu_t % f_{\weights_{s}}(\MZ_s)
	\right\rVert_{\bar{\MB}^{-1}_{s}}.
\end{equation}

>>>>

After each task, we update $\mathcal{M}$, and we can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s = 1, \ldots, t-1$. This means that for training  the successive task, the new objective to minimize becomes $\weights_t^* = \arg\min_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \, \mathcal{R}_\textrm{\our}(\weights, \mathcal{M})$, with the regularizer
%
\begin{equation}\label{eq-cl-regularizer}
  \mathcal{R}_\mathrm{\our}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \frac{1}{M} 
	\left\lVert 
	f_{\weights}(\MZ_{s}) - \vu_t % f_{\weights_{s}}(\MZ_s)
	\right\rVert_{\bar{\MB}^{-1}_{s}}.
\end{equation}
